---
title: "Hello R Markdown"
author: "Frida Gomam"
date: 2021-11-01
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r include=FALSE}

re_data <- read.csv("~/Desktop/real_estate.csv", sep="")
str(re_data)

#Change to factors  

names_factor <- c('PostedBy', 'UnCon', 'RERA', 'ToP', 'RtM', 'RoN')
re_data[,names_factor] <- lapply(re_data[,names_factor] , factor)

#Change to numbers  

names_num <- c('NoR', 'NoS', 'NoP')
re_data[,names_num] <- lapply(re_data[,names_num] , as.numeric)
 
summary(re_data)

re_data<-re_data%>%
  mutate(Long=Latitude, Lat=Longitude)%>%
  dplyr::select(.,-c('Latitude','Longitude','fit.cluster'))
```

# 2. Create a subset from the dataset

## Create a new factor variable Country using map.where() from the package "map"

(use the R help to see how to use map.where())

```{r include=FALSE}

library(maps)
#create variable country using map.where() from the package "maps"

re_data<-re_data%>%
  mutate(Country=as.factor(map.where(x = Long, y = Lat)))

```

## table summarizing the number of observations per country

```{r include=FALSE}
summary(re_data$Country)
table(re_data$Country)

```

#select observations only in india

```{r include=FALSE}
re_india<-re_data%>%
  filter(Country=="India")
summary(re_india)
```

## Remove the observations with missing values

```{r include=FALSE}
re_india<-re_india%>%
  na.omit(.)
```

# link the longitude and latitude with Indian regions using getData() from the package "raster"

```{r include=FALSE}
india_level1 = raster::getData("GADM", country = "IND", level = 1)  
```

2. Extract the attributes from the shapefile for the given points

We can use the function extract()

```{r include=FALSE}
region_names = raster :: extract(india_level1, re_india[, c("Long", "Lat")])
region_names = region_names [,"NAME_1"]
```

3.  Adding the region names to the Indian data frame, with the coordinates

```{r include=FALSE}
re_india$Region = as.factor(region_names)
summary(re_india$Region)
```

# 3. Explore and develop a focus question

-   What is the average price, rooms number, size, number of supermarket or park around the property?
-   What is the distribution of prices?
-   How does the price depend on the size of the house?
-   Does new construction influence the price?
-   How does the number of rooms influence the price?
-   How does the number of supermarkets influence the price?
-   How does the number of parks influence the price?
-   Does the region influence price?

## What is the average price, rooms number, size, number of supermarket or park around the property?

```{r echo=FALSE, message=FALSE, warning=FALSE}
round(colMeans(re_india[,c('Price','NoR','Size','NoS','NoP')]),1) 
```

## What is the distribution of prices?

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)

ggplotly(ggplot(data=re_india) +
  geom_histogram(mapping=aes(Price), binwidth = 100, boundary=100, colour="grey")+
#grey for the outline
  scale_x_continuous(breaks = seq(from = 100, to = 4900, by = 400), limits = c(100, 4900))+
  ylim(0,2500)+
  ggtitle("Histogram of Price")+
  theme(plot.title = element_text(hjust = 0.5,face="bold")) 
) 
  

```

## How does the price depend on the size of the house?

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplotly(ggplot(data=re_india)+
  geom_point(mapping=aes(y=Price,x=Size))+
  scale_x_continuous(breaks = seq(from = 0, to = 22000, by = 2000), limits = c(0, 22050))+
  ggtitle("Size vs Price of properties, India, 2020")+
  theme(plot.title = element_text(hjust = 0.5,face="bold"))+
  labs(x="Size (in sq ft)",y="Price (in thousands INR)")
)
```

## How does the construction status(new construction) influence the price?

```{r echo=FALSE, message=FALSE, warning=FALSE}
re_india<-re_india %>%
  mutate(Status=ifelse(UnCon==0,"Constructed","Under construction"))

ggplotly(re_india %>%
  filter(Size<5000) %>%
  ggplot()+
  geom_point(mapping=aes(y=Price,x=Size,colour=Status))+
  ggtitle("Size vs Price of properties per construction status, \n India, 2020 (Size < 5000 sq ft)")+
  theme(plot.title = element_text(hjust = 0.5,face="bold"))+
  labs(x="Size (in sq ft)",y="Price (in thousands INR)")
  )

```
